A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2025-07-20 paper/paper.tex
Rewording to preserve a paragraph

Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets.

Using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$. Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$. This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.

>>>>

Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets. Using the notations of Section~\ref{sec:tt} and of the Appendix, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the dependent stream given by $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$. Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$. This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
